\documentclass[11pt]{article}
\title{resume}
\usepackage{hyperref}
\usepackage{color}
\usepackage{charter}
\topmargin=-0.6in
\oddsidemargin=-0in
\evensidemargin=0in
\usepackage[none]{hyphenat}
\textwidth=6.5in
\marginparwidth=0.5in
\headheight=0pt
\headsep=0pt
\textheight=9.0in
%\usepackage[bottom=0.5in,top=0.5in]{geometry}
\pagenumbering{gobble}
\usepackage[margin=0.7in]{geometry}
\newcommand\phv{\fontfamily{bch}\selectfont}
\newcommand\qcr{\fontfamily{qcr}\selectfont}
\begin{document}
\centerline{{\Huge \bf \phv{Sam Burdick}}}
\noindent\\
\centerline{
{\textcolor{blue}{\href{https://smburdick.github.io/}{Website}} \hspace{1.5pt} $|$ \hspace{1.5pt}
\textcolor{blue}{\href{https://github.com/smburdick}{GitHub}}
}}
\centerline{{smburdick@pugetsound.edu}}
\centerline{18127 Miss Ellis Loop NE, Poulsbo, WA 98370 $|$ (425) 275-8685}
%\centerline{1234 Generic St. \textbullet \hspace{5pt}   Boulder, CO 80303 \textbullet \hspace{5pt}   (555) 555-0198}
% \\\noindent\line(1,0){470}
\\\\
\noindent {\LARGE \bf \phv{\underline{Objective}}}
\begin{itemize}
\item Pursuing a challenging internship in software development where strong programming skills will be of service.
\end{itemize}
\vspace{0.4cm}
\noindent{\LARGE \bf \phv{\underline{Work Experience}} }  \medskip\\
\noindent \centerline{\large \bf Independent Contractor for Coffee Production Application and Company Website \hfill }
\\
\emph{ {\textcolor{blue}{\href{http://candacesoft.com}{Candace Software}}, Lynnwood, WA. Jun. 2016 - present}}
\begin{itemize}
  \item Co-developed an application that generates and displays data reports pertinent to coffee producers using Visual C\# and MySQL
  \item Collaborated on software solutions with team members in Lynnwood and Addis Ababa for this coffee production technology startup
  \item Creating company webpage to help recruit new talent for the company
\end{itemize}
\vspace{0.2cm}
\noindent \centerline{\large \bf Application Developer for {\textcolor{blue}{\href {https://tmfsa.herokuapp.com/}{AUTOMATA}} online learning environment \hfill  }}
\\\emph{Collaboration with \textcolor{blue}{\href{http://mathcs.pugetsound.edu/~tmullen/}{Professor Tony Mullen}}, Dec. 2016 - present}
\begin{itemize}
\item Implementing editing features to enhance the user experience of a hands-on automaton theory learning MEAN.js application
\vspace{0.2cm}
% \item Gaining practice writing code to specifications
\end{itemize}
%\noindent \centerline{\large \bf Online {\textcolor{blue}{\href{https://smburdick.github.io/threejs-raytracer}{Ray Tracer}} \hfill }}
%\\\emph{Computer Graphics final project. Dec. 2016}
%\begin{itemize}
%	\item Created a ray tracer using THREE.js and implemented depth of field, soft shadows, and antialiasing features, aided by my linear algebra experience
%\end{itemize}
\noindent \centerline{\large \bf Teaching Assistant for Introduction to Computer Science \hfill }
\\\emph{University of Puget Sound. Sept. 2016 - present}
\begin{itemize}
  \item Answering student questions in weekly lab sessions, grading Java assignments, and helping solve programming problems in walk-in tutoring hours
  \item Developing communication skills by interacting with students and coordinating with the instructor to ensure students' success in and satisfaction with the course
\end{itemize}
\vspace{0.2cm}
% \noindent\centerline{\large\bf }
\noindent \centerline{\large \bf Team Collaborator on ``Schedule Master'' web application \hfill }
\\\emph{Software Engineering course group project. May 2016}
\begin{itemize}
  \item Created a MEAN.js application that helps students find their classes on campus
  \item Designed and implemented the course information database and the user class selection interface
  \item Gained leadership experience by providing UI design oversight and task prioritization
\end{itemize}
\vspace{0.4cm}
\noindent{\LARGE \bf \phv{\underline{{Education \& Technology} }} }
\begin{itemize}
  \item University of Puget Sound, Computer Science and Mathematics double major, 3.65 cum. GPA, expected to graduate May 2018
  \item Proficient in Java, C\#, MySQL, JavaScript, HTML, CSS, Angular, Node
\end{itemize}

\end{document}
