\documentclass[11pt]{article}
\title{resume}
\usepackage{hyperref}
\usepackage{color}
\usepackage{charter}
\topmargin=-0.4in
\oddsidemargin=-0in
\evensidemargin=0in
\textwidth=6.5in %How wide you want your text to be
\marginparwidth=0.5in
\headheight=0pt %1in margins at top and bottom (1 inch is added to this value by default)
\headsep=0pt %Increase to increase white space in between headers and the top of the page
\textheight=9.0in %How tall the text body is allowed to be on each page
\pagenumbering{gobble}
\newcommand\phv{\fontfamily{phv}\selectfont}
\newcommand\qcr{\fontfamily{qcr}\selectfont}
\begin{document}
% TODO: eliminate passive voice AMAP,
\centerline{{\Huge \bf \phv{Sam Burdick}}}    % (want sc?)
\noindent\\
\centerline{
{\textcolor{blue}{\href{https://smburdick.github.io/}{Website}} \hspace{1.5pt} $|$ \hspace{1.5pt}
\textcolor{blue}{\href{https://github.com/smburdick}{GitHub}}
}}
\centerline{{smburdick@pugetsound.edu}}
 % TODO: align links + email on one line?
%\centerline{1234 Generic St. \textbullet \hspace{5pt}   Boulder, CO 80303 \textbullet \hspace{5pt}   (555) 555-0198}
% \\\noindent\line(1,0){470}
\\\\
\noindent {\LARGE \bf \phv{Summary}}   %Don’t indent this line and make it bold and large
\medskip\\
\noindent
% \bigskip %This makes a large line-skip (\smallskip is also a command but has a smaller gap
% \\
% \noindent{\Large \bf Executive Summary}
% \\\\
% \smallskip
% \noindent
Upcoming graduate in Computer Science pursuing a strong mathematical foundation and practical development experience. My contributions to solving programming problems with teams and individuals make me a highly qualified software developer candidate. \\\\
\smallskip
\noindent{\LARGE \bf \phv{Work Experience} }  \medskip\\
\noindent \centerline{\large \bf {\textcolor{blue}{\href{https://tmfsa.herokuapp.com/}{AUTOMATA}} Environment app development \hfill  }}
\\\emph{Dec. 2016 - present}
\begin{itemize}
\item Implementing editing features to enhance the user experience of \textcolor{blue}{\href{http://mathcs.pugetsound.edu/~tmullen/}{Tony Mullen}}'s hands-on automaton theory learning MEAN.js app
% \item Gaining practice writing code to specifications
\end{itemize}
\noindent \centerline{\large \bf Online {\textcolor{blue}{\href{https://smburdick.github.io/threejs-raytracer}{Ray Tracer}} \hfill }}
\\\emph{Computer Graphics final project. Dec. 2016}
\begin{itemize}
	\item Created a ray tracer using THREE.js and implemented depth of field, soft shadows, and antialiasing features, aided by my linear algebra experience
\end{itemize}
\noindent \centerline{\large \bf Intro to Computer Science Teaching Assistant \hfill }
\\\emph{University of Puget Sound. Sept. 2016 - present}
\begin{itemize}
  \item I answer student questions in weekly lab sessions, grade Java assignments, and help solve programming problems in walk-in tutoring hours
  \item Developed communication skills from interacting with students and coordinating with the instructor to ensure students' success in and satisfaction with the course
\end{itemize}
\noindent \centerline{\large \bf Independent Contractor for Coffee Production Application \hfill }
\\\emph{Candace Research, Lynnwood, WA. Jun. 2016}
\begin{itemize}
  \item Generates and displays data reports pertinent to coffee producers using Visual C\# and MySQL
  \item Obtained software solutions with team members in Lynnwood and Addis Ababa for an importer and distributor of Ethiopian coffee
\end{itemize}
% \noindent\centerline{\large\bf }
\noindent \centerline{\large \bf ``Schedule Master'' web app development \hfill }
\\\emph{Software Engineering course group project. May 2016}
\begin{itemize}
  \item Created a MEAN.js app that helps students find their classes on campus
  \item Designed and implemented the course info database and the user class selection interface
  \item Gained leadership experience by providing UI design oversight and task prioritization when we weren't making deadlines
\end{itemize}
\noindent{\LARGE \bf \phv{Education \& Technology}  }
\begin{itemize}
  \item University of Puget Sound, Computer Science and Mathematics double major, 3.65 cum. GPA
  \item Proficient in Java, C\#, MySQL, JavaScript, HTML, CSS, Angular, Node
\end{itemize}

\end{document}
